Language-Based Low-Level MPC Security: $\metaprot$ to $\minifed$

### 2024-05-13 ppdp24/examples.tex
checkpoint

>>>>

Eliminating cheating by adding information theoretic secure MAC codes
to shares is a fundamental approach realized by protocols such as BDOZ
\cite{XXX} and SPDZ \cite{XXX}.  These protocols assume a
pre-processing phase that distributes shares with MAC codes to
clients.  This integrates well with pre-processed Beaver Triples to
implement malicious secure, and relatively efficient, multiplication
\cite{XXX}.  Here we show how to implement malicious secure two party
multiplication in the BDOZ style via some extensions of $\minifed$.

A field value $v$ is secret shared among 2 clientz in BDOZ as follows.
Each client $\cid$ gets a pair of the form $(v_\cid,m_\cid)$, where
$v_\cid$ is a secret share of $v$, i.e., $v = \fcod{v_1 \fplus v_2}$.
Further, field values $m_\cid$ are MACs of $v_\cid$ that are authenticated
by the other client's key. In particular, $m_\cid = k + (k_\Delta *
v_\cid)$ where \emph{keys} $k$ and $k_\Delta$ are known only to $\cid'
\ne \cid$ and $k_\Delta$. Further, there is a unique \emph{local key}
$k$ for each shared value, while the \emph{global key} $k_\Delta$ is
common to all MACs authenticated by $\cid'$. By extending certain
field operations to these MACed values, a semi-homorphic encryption
scheme is obtained that is adequate to compute Beaver Triples. For
example, if local keys $k_1$ and $k_2$ authenticate $\macv_1$ and
$\macv_2$, then $k_1 \fplus k_2$ authenticates $\macv_1 \macplus
\macv_2$, where $\macplus$ is addition extended to MACed
values. Semantics for summation of MACed shares, and multipication of
shares and plain field values, are given in Figure \ref{fig-bdoz}.
For more details the reader is referred to \cite{XXX}. We note
that while we restrict values $v$, $m$, and $k$ to the same
field in this presentation for simplicity, in general $m$ and
$k$ can be in extensions of $\mathbb{Z}_p$.

We define variable forms $\macx{\secret{w}}{\cid}$ and
$\macx{\flip{w}}{\cid}$ to range over local MACed shares of a secret
and random sample owned by client $\cid$, respectively. We let
$\mack{x}{}$ denote the local key for authenticating shares of $x$.
We also assume a global key $\flip{\ttt{delta}}$ on each client.
Pre-processing is modeled by assuming that shares are provided on
input random tapes (memories) with the required properties, as defined
on the bottom of Figure \ref{fig-bdoz}.

Similarly to field values, we can use MACed shares in
uniform independent distributions as one-time-pads for
hiding other values, using subtraction over MACed shares.
So we introduce a function $\macotp$ to do this
declaratively.
$$
\delta(\macotp,v_1,v_2) \defeq \fcod{v_1 \macminus v_2}
$$

Another key idea in BDOZ is \emph{secure opening}, where distributed
shares of a value $v$ are communicated and combined to ``open'' the
same $v$ on each client. This relies on authentication to detect
cheating in the malicious setting. To implement secure opening we
define a $\macauth$ function that authenticates shares, and a
$\macopen$ function that extracts a field value from its shares.
\begin{mathpar}
\delta(\macauth, (v, m), k) \defeq
     (v, m) \text{\ if\ } m = k \fplus (\flip{\ttt{delta}} \ftimes v)

\delta(\macopen, (v_1, m_1), (v_2,m_2)) \defeq
\fcod{v_1 \fplus v_2}
\end{mathpar}
This authentication eliminates cheating and guarantees protocol
integrity. As we will show in Section \ref{section-types}, this
can be reflected in a security type for $\macauth$.

Putting these pieces together, we can implement 2-party multiplication with
Beaver Triples as follows. Recall that Beaver Triples are values
$(a,b,c)$ such that $c = \fcod{b \ftimes a}$- we implement them here
as a secret $\secret{c}$ and samples $\flip{a}$ and $\flip{b}$ owned
by an \emph{oracle} $\Oracle$ that we always assume is honest but is
otherwise not involved in the protocol. We define pre-processing
properties of Beaver Triples in Figure \ref{fig-bdoz}. Only one
Beaver triple can be used per multiplication to ensure secure
openings, but our scheme can be extended with more Beaver triples
and reuse of them will be rule out by type linearity as we will
discuss in Section \ref{section-types}.

First, clients 1 and 2 compute (aka \emph{open}) $\secret{x} \fplus
\flip{a}$ and $\secret{y} \fplus \flip{b}$ where $\secret{x}$ and
$\secret{y}$ are 1 and 2's secrets respectively.  Then they both
perform a secure opening of $\secret{x} \fplus \flip{a}$ and
$\secret{y} \fplus \flip{b}$, by authenticating each others' shares,
and record them as $\mesg{d}$ and $\mesg{e}$ respectively. Note
that the secrets remain hidden since $\flip{a}$ and $\flip{b}$
are random values.
